Haider Data Figures

### 2024-01-22 R/23_02_02_real_data_rice.Rmd
24_01_22_1

---
title: "Haider Data Demo"
author: "Fred White"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::html_document2:
    toc: true
    theme: united
    toc_depth: 3
---

>>>>

---
title: "Haider Data Figures"
author: "Fred White"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::html_document2:
    toc: true
    theme: united
    toc_depth: 3
---
